Social Visual Analytics: DevOps for Data Scientists

### 2015-03-20 introduction.tex
fix weird ligatures in quote document

% \begin{addmargin}[1em]{1em}  % left and right margin change
% part1.txt
Erin Shellman [of Nordstrom] described the benefits of
continuous deployment of experiments, and sharing knowledge
through software and data analysis artifacts.
``Finally, prototyping our products so that internal
customers can use them early on has been crucial for
our success. It doesn't even have to be something
fancy. For instance, our recommendations preview
tool doesn't have a particularly interesting
visualization, but its enough to show the result of our
algorithms. Now we can shoot off a URL to internal
customers and it allows them to sit at their desk and
understand the behavior of our product and
experiment with it, and provide feedback way before
we're talking about getting it into production. This
has been super helpful and has been a really great
way to get people excited about what we're working
on...
%Building and maintaining those relationships are
%just like anything else-- you always have to be
%working on them. Nurturing those relationships are
%part of the job, and if you leave them unattended,
%they might not be there later.
%
% part2.txt
%Gutierrez: How do you share the knowledge you are
%building with others?
We’re obsessed with Confluence from
Atlassian, and the Data Lab has a very active
Confluence space. Recommendo is fully documented
on Confluence, so anyone in the company could learn
how it’s built, where to find it, and how to use it.
We also share exploratory analyses and reports on
Confluence so that we can still exchange knowledge
even if the work didn’t make it into a larger project.''

% part3.txt
John Foreman commented on the scope of the work in
data science teams.
``I lead the data science team at
MailChimp, and I like to get my hands dirty too.
Some of the big pieces of my day involve working
with my team to take stock of current projects and
figure out where to go next, doing my own work and
prototyping things-- I do projects just like my peers
do and then also my talking with other teams,
talking with management, and planning for the
future.
On our team, we’ve got different folks facing different
% part4.txt
kinds of projects. We’ve got one person who really
owns compliance and looks at our compliance
processes. We’ve got another data scientist who
focuses on more of the user experience side of the
house and understanding our customers. I help them
and others as is needed while I do the three things
mentioned earlier-- build data products, be a
translator, and have conversations with the data
science community.''

% part5.txt
Jonathan Lenaghan from PlaceIQ discussed to the potential
for continous deployment in data science.
``If you look at dev ops right now, they have things
such as continuous integration, continuous build,
automated testing, and test harnesses-- a1l of which
map very well from the dev ops world to the data ops
(a phrase I stole from Red Monk) world very easily. I
think this is a very powerful notion. It is important to
have testing frameworks for all of your data, so that if
you make a code change, you can go back and test all
of your data.''

>>>>

% \begin{addmargin}[1em]{1em}  % left and right margin change
% part1.txt
Erin Shellman [of Nordstrom] described the benefits of
continuous deployment of experiments, and sharing knowledge
through software and data analysis artifacts.
``Finally, prototyping our products so that internal
customers can use them early on has been crucial for
our success. It doesn't even have to be something
fancy. For instance, our recommendations preview
tool doesn't have a particularly interesting
visualization, but its enough to show the result of our
algorithms. Now we can shoot off a URL to internal
customers and it allows them to sit at their desk and
understand the behavior of our product and
experiment with it, and provide feedback way before
we're talking about getting it into production. This
has been super helpful and has been a really great
way to get people excited about what we're working
on...
%Building and maintaining those relationships are
%just like anything else-- you always have to be
%working on them. Nurturing those relationships are
%part of the job, and if you leave them unattended,
%they might not be there later.
%
% part2.txt
%Gutierrez: How do you share the knowledge you are
%building with others?
We’re obsessed with Confluence from
Atlassian, and the Data Lab has a very active
Confluence space. Recommendo is fully documented
on Confluence, so anyone in the company could learn
how it’s built, where to find it, and how to use it.
We also share exploratory analyses and reports on
Confluence so that we can still exchange knowledge
even if the work didn't make it into a larger project.''

% part3.txt
John Foreman commented on the scope of the work in
data science teams.
``I lead the data science team at
MailChimp, and I like to get my hands dirty too.
Some of the big pieces of my day involve working
with my team to take stock of current projects and
figure out where to go next, doing my own work and
prototyping things-- I do projects just like my peers
do and then also my talking with other teams,
talking with management, and planning for the
future.
On our team, we've got different folks facing different
% part4.txt
kinds of projects. We've got one person who really
owns compliance and looks at our compliance
processes. We've got another data scientist who
focuses on more of the user experience side of the
house and understanding our customers. I help them
and others as is needed while I do the three things
mentioned earlier-- build data products, be a
translator, and have conversations with the data
science community.''

% part5.txt
Jonathan Lenaghan from PlaceIQ discussed to the potential
for continuous deployment in data science.
``If you look at dev ops right now, they have things
such as continuous integration, continuous build,
automated testing, and test harnesses-- a1l of which
map very well from the dev ops world to the data ops
(a phrase I stole from Red Monk) world very easily. I
think this is a very powerful notion. It is important to
have testing frameworks for all of your data, so that if
you make a code change, you can go back and test all
of your data.''
